\documentclass{article}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[sort&compress,comma,authoryear]{natbib}
\newcommand{\Prob}[0]{\mbox{Prob}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\usepackage{bm}
\usepackage{latexsym}


\title{DEB model description: `hep'}
%\author{S.A.L.M. Kooijman and K. Lika and S. Augustine and N. Marn and others?}


\begin{document}

\maketitle

This document specifies the typified DEB model  `hep' \citep{MarqAugu2018}.
The `hep' typified model is a {\sc deb} model for hemi-metabolic insects, such as ephemeropterans, odonata and possibly other insect groups. Its characteristics are:
\begin{itemize}
\item morphological life stages: egg, larva, (sub)imago; functional stages: embryo, juvenile, adult, imago
 \item    the embryo still behaves like model std
\item acceleration starts at birth and ends at puberty
\item  puberty occurs during the larval stage
\item emergence occurs when reproduction buffer density hits a threshold
\item the (sub)imago does not grow or allocate to reproduction. It mobilises reserve to match constant (somatic plus maturity) maintenance
\end{itemize}
Nymphs of \href{https://en.wikipedia.org/wiki/Mayfly}{Mayflies (ephemeropterans)} transform into flying \href{https://en.wikipedia.org/wiki/Mayfly#Subimago}{subimagos}, which subsequently transform into \href{https://en.wikipedia.org/wiki/Imago}{imagos} within minutes till 3 days (depending on species and temperature).
Imagos live several days, and, like subimagos, don't feed, implying that nymphs allocate to reproduction.
Ephemeropterans are presently the only insects that moult (once) while having wings.
The hep model also applies to Odonata and possibly some other groups as well.

To capture this pattern the hep model assumes that type $\cal M$ acceleration \citep[section 3.3]{Kooy2014} occurs between birth (event $b$) and puberty (event $p$), and transformation to subimago occurs when the reproduction buffer exceeds a threshold (event $j$), called $[E_R^j]$. 
So (isomorphic) growth occurs in the adult nymph, but not in the (sub)imago.
We assume that the heating length is zero, i.e.\ $L_T = 0$, so $l_T = 0$ as well.

Allocation to reproduction at constant food amounts to $\frac{d} {dt} E_R = \dot{p}_R =  (1 - \kappa) \dot{p}_C  - \dot{p}_J $, with reserve mobilisation $\dot{p}_C = [E_m] L^3 (\frac{\dot{v} s_{\cal M}} {L} + \dot{k}_M) \frac{e g} {e + g}$, maturity maintenance $\dot{p}_J = \dot{k}_J E_H^p$, acceleration factor $s_{\cal M} = L_p/ L_b = l_p/ l_b$.
If emergence would not kick in, $L \rightarrow L_\infty = s_{\cal M} f L_m$ and the reproduction buffer density grows at constant rate $\frac{d} {dt} [E_R] \rightarrow \frac{1 - \kappa} {\kappa} [\dot{p}_M] - \frac{\dot{p}_J} {L_\infty^3}$. 
The change in reproduction buffer density is $\frac{d} {dt} [E_R] = [\dot{p}_R] - 3 \dot{r}_B (L_\infty/ L - 1) [E_R]$.
Since reproduction buffer density starts at zero at event $p$, we are sure that it hits any finite threshold, but we need to find the first event as long as $(1 - \kappa) [\dot{p}_M] L_\infty^3 > \kappa \dot{p}_J$, to allow for puberty to be reached.
%In the hex model (see next section), the reproduction buffer density has a maximum, due to acceleration, and therefore does not hit a threshold value for sure.

At constant food density, scaled length changes in scaled time as $\frac{d} {d \tau} l = r_B(l_\infty - l)$ or $l(\tau) = l_\infty - (l_\infty - l_p) \exp(r_B \tau)$ with scaled $r_B = (3 + 3 f/g)^{-1}$ and $l_\infty = s_{\cal M} f$.
The dimensionless scaled reproduction buffer density $v_R = \frac{\kappa} {1 - \kappa} \, \frac{[E_R]} {[E_G]}$ changes as 
$\frac{d} {d \tau} v_R = \frac{f g s_{\cal M}/ l + f} {g + f} - \frac{k v_H^p} {l^3} - 3 r_B v_R (f s_{\cal M} / l - 1)$.
So scaled time at emergence is $\tau_j = \int_0^{v_R^j} \frac{d} {d v_R} \tau$ and $l(0) = l_p$ and $l(\tau_j) = l_j$ with  $v_R^j = \frac{\kappa} {1 - \kappa} \, \frac{[E_R^j]} {[E_G]}$. 
The number of eggs at emergence is $N = \kappa_R [E_R^j] L_j^3/ E_0 = (1 - \kappa) \kappa_R v_R^j l_j^3/ u_E^0$




\section{Background}

\input{model_intro}

\input{std_description}

\bibliographystyle{apalike}
\bibliography{debmodels}

\end{document}