\documentclass{article}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[sort&compress,comma,authoryear]{natbib}
\newcommand{\Prob}[0]{\mbox{Prob}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\usepackage{bm}
\usepackage{latexsym}


\title{DEB model description: 'sbp'}
%\author{S.A.L.M. Kooijman and K. Lika and S. Augustine and N. Marn and others?}


\begin{document}

\maketitle

This document specifies the standard DEB model 'std'.
This model belongs to the class of s-models which assumes isomorphy throughout the full life cycle.
The following section provides an overiew of how the 'std' fits within a wider framework of DEB related models before technically specifying the std model.
The 'sbp' model is like the 'std' except that: 
\begin{description}
  \item[$\circ$] growth ceases at puberty, meaning that the $\kappa$-rule is not operational in adults.   
\end{description}
It has the same parameters as the std-model, and is similar to the abp-model, which differs by acceleration.
This life history is found in \emph{Calanus}, while other copepods accelerate. 

At puberty, growth ceases. so $\dot{p}_G = 0$, and the $\kappa$-rule no longer applies. 
Mobilisation after puberty is $\dot{p}_C = \dot{v} E/ L_p$, 
  and allocation to reproduction is $\dot{p}_R = \dot{p}_C - \dot{p}_M - \dot{p}_J$, with $\dot{p}_J = \dot{k}_J E_H^p$.s the standard DEB model 'sbp'.
This model belongs to the class of s-models which assumes isomorphy throughout the full life cycle.
Like the std-model but with 

\section{Background}

\input{model_intro}

\input{std_description}

\bibliographystyle{apalike}
\bibliography{debmodels}

\end{document}